Proof nets for first-order additive linear logic

### 2018-01-17 ALL1.tex
aargh try again

\begin{document}

\begin{lemma}
For $\link ab$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}=\mgu(a,c)$.
\end{lemma}

\begin{proof}
Let $\rho=\mgu(a,c)$ and $\rho'=\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$. Define the \defn{basis} $\floor{s,t}$ of the $\mgu$ of $s$ and $t$ to be the substitution map defined by $\floor{x,t}=\floor{t,x} = [t/x]$ and
\[
	\floor{P(s_1,\dots,s_n),P(t_1,\dots,t_n)} =
	\floor{f(s_1,\dots,s_n),f(t_1,\dots,t_n)} =
	\floor{s_1,t_1}\dots\floor{s_n,t_n}~.
\]
Write $\floor\sigma$ for the basis $\floor{a,b}$ of $\sigma$, $\floor\tau$ for that of $\tau$, and $\floor\rho$ for that of $\rho$.
\end{proof}

>>>>

\begin{document}
%
%\begin{lemma}
%For $\link ab$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}=\mgu(a,c)$.
%\end{lemma}
%
%\begin{proof}
%Let $\rho=\mgu(a,c)$ and $\rho'=\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$. Define the \defn{basis} $\floor{s,t}$ of the $\mgu$ of $s$ and $t$ to be the substitution map defined by $\floor{x,t}=\floor{t,x} = [t/x]$ and
%\[
%	\floor{P(s_1,\dots,s_n),P(t_1,\dots,t_n)} =
%	\floor{f(s_1,\dots,s_n),f(t_1,\dots,t_n)} =
%	\floor{s_1,t_1}\dots\floor{s_n,t_n}~.
%\]
%Write $\floor\sigma$ for the basis $\floor{a,b}$ of $\sigma$, $\floor\tau$ for that of $\tau$, and $\floor\rho$ for that of $\rho$.
%\end{proof}
%
%\end{document}
%
